Preliminary insights into the use of pottery and culinary practices at Guijiabao site in southwest China

### 2024-02-16 analysis/paper/paper.Rmd
submitted to ARA

---
title: "Preliminary insights into the use of pottery and culinary pratices at Guijiabao site in southwest China"
author:
  - Li-Ying Wang:
      email: liyingw@asihp.net
      institute: [AcS]
      correspondence: true
  - Kuei-chen Lin:
      email: kueichenlin@asihp.net
      institute: [AcS]
      correspondence: false
  - Zhiqing Zhou:
      email: zhouzhiQ2000@163.com
      institute: [InsC]
      correspondence: false
institute:
  - AcS: Institute of History and Philology, Academia Sinica 
  - InsC: Chengdu Institute of Cultural Relics and Archaeology
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |

     Mixed crops of millet and rice are thought to have been introduced to southwest China in the Neolithic period. Despite the recovery of both millet and rice grains, the varying proportions observed across the area underscore the complexity of the process of agricutural dispersal. Further investigation is needed to understand how new crops were integrated into southwest China, characterized by diverse environmental conditions and landscapes. This study contributes to this understanding by exploring subsistence strategies in southwest Sichuan through a preliminary analysis of lipid residues in pottery from the Guijiabao site using organic geochemical analyses. The site, situated in the middle Hengduan mountain ranges, presents well-preserved stratigraphic records spanning from the Neolithic to the historical period, providing valuable insights into local subsistence practices in a highland environment. Results reveal the detection of ruminant adipose fats in the majority of potsherds, with a few showing plant inputs such as broomcorn millet. This suggests that animals played a substantial role in the local diet, alongside the consumption of millet. These culinary practices also indicate that hunting may have remained a significant subsistence activity in the high-altitude region of southwest China, even after the introduction of crops.

>>>>

---
title: "Preliminary insights into the use of pottery and culinary practices at Guijiabao site in southwest China"
author:
  - Li-Ying Wang:
      email: liyingw@asihp.net
      institute: [AcS]
      correspondence: true
  - Kuei-chen Lin:
      email: kueichenlin@asihp.net
      institute: [AcS]
      correspondence: false
  - Zhiqing Zhou:
      email: zhouzhiQ2000@163.com
      institute: [InsC]
      correspondence: false
institute:
  - AcS: Institute of History and Philology, Academia Sinica 
  - InsC: Chengdu Institute of Cultural Relics and Archaeology
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |

     Mixed crops of millet and rice are thought to have been introduced to southwest China in the Neolithic period. Despite the recovery of both millet and rice grains, the varying proportions observed across the area underscore the complexity of the process of agricultural dispersal. Further investigation is needed to understand how new crops were integrated into southwest China, characterized by diverse environmental conditions and landscapes. This study contributes to this understanding by exploring subsistence strategies in southwest Sichuan through a preliminary analysis of lipid residues in pottery from the Guijiabao site using organic geochemical analyses. The site, situated in the middle Hengduan mountain ranges, presents well-preserved stratigraphic records spanning from the Neolithic to the historical period, providing valuable insights into local subsistence practices in a highland environment. Results reveal the detection of ruminant adipose fats in the majority of potsherds, with a few showing plant inputs such as broomcorn millet. This suggests that animals played a substantial role in the local diet, alongside the consumption of millet. These culinary practices also indicate that hunting may have remained a significant subsistence activity in the high-altitude region of southwest China, even after the introduction of crops.
